MINOS Handover Plots

### 2023-03-16 minos/validation/handovers.Rmd
Improve the logic for reading in final_US files, so that it ignores any directories in the folder (i.e. cross-validation dir)

```{r}
# Read raw datafiles in
raw.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/final_US/', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

>>>>

```{r}
# Read raw datafiles in
raw.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/final_US/', pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
